% -*- mode: LaTeX; mode: flyspell; -*-
% mode: Tex-Pdf -*-
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage[bookmarks=TRUE,
            colorlinks,
            pdfpagemode=none,
            pdfstartview=FitH,
            citecolor=black,
            filecolor=black,
            linkcolor=blue,
            urlcolor=black,
            ]{hyperref}
\usepackage{graphicx}
\usepackage{icomma}
\usepackage[utf8]{inputenc}
\usepackage{natbib}

\pagestyle{empty}

\begin{document}

\section*{Data Confidentiality Agreement}

Court records' analysis involves working with personal data--the court
records that contain personal information, such as names, addresses,
and details about the court cases.  Although the courts cases are
public, we treat such information, when collected in bulk, as
confidential data.

By signing this document I agree with the following:
\begin{itemize}
\item I acknowledge that \emph{all}  data I may obtain when working
  within this project, and that contains any personal identifiable
  information will be treated as confidential.
\item I agree not to share any such data with others without explicit
  permission from faculty members (Bill Howe or Ott Toomet).  This
  includes sharing data with other workgroup members.
\item I agree to take reasonable steps to avoid data being stolen, or
  being accessed by unautorized people.  I will
  \begin{itemize}
  \item keep data only on my personal computer(s), or dedicated
    servers. 
  \item not upload it to any publicly accessible website, such as
    google drive that is accessible for everyone.  (Sharing on web
    with only selected people is ok).
  \item I will delete the data if I am not a part of the project any
    more, or if I will give away the computer where the
    data is stored. 
  \end{itemize}
\item I agree not to share images or summaries the contain
  personally identifiable information, without
  explicit permission from faculty members (Bill Howe or Ott Toomet),
  with people
  outside of the research group.
\end{itemize}

\bigskip

Seattle, \today

\vspace{15mm}

Name: \hbox to 8cm{\leaders\hbox to 10pt{\hss . \hss}\hfil}


\vspace{15mm}

Signature:


\bibliographystyle{econometrica}
\bibliography{Economics}

\end{document}
